	PURPOSE:  Collect all notes, links, references for R to here.
	NO installation (R, Rstudio, etc) in this file

<!--
KEEP as .qmd file
-->

## Compare
```{r}
#| echo: true
#| eval: false
a=c(1,1,1)
b=c(2,2,2)
`+`(a,b)
a+b
sum(a+b)
```   
```{r}
#| echo: false
#| eval: true
a=c(1,1,1)
b=c(2,2,2)
`+`(a,b)
a+b
sum(a+b)
```



**AST**
Diagram expression into various parts (calls, symbols, constants?)
Metacode refers to manipulation of this tree.
NSE refers to tinker with how fct evaluates arguments.

**attach**
    - add df/list/datafile/env to *search list*, at a `pos` and `name`
    - for database, can access column names, unquoted.
	- detach(mtcars) to remove from search list
    - compare to `with`
      - https://stat.ethz.ch/R-manual/R-devel/library/base/html/attach.html
```{r}
search()

mtcars
# hp   # object 'hp' not found

# add to search list
?attach
attach(mtcars)
search()
hp  # no error

# remove 
detach(mtcars)

# remove package 
search()
```
explain process:  capture unevaluated code; manipulate it; later evaluate

-	defuse, substitution, quasiquotation, 
-	injection (into unevaluated expression)
-	defuse &  inject are opposites
-	embrase {{}}, tells function must first evalute the unevaluated content inside {{}}

**bindings:**
-   link between name (symbol) and an object
-   EX:   f (name) and the definition (function(x) {...})
-   https://r-pkgs.org/dependencies-mindset-background.html#sec-dependencies-search

**bquote**  SEE String Interpolation
**Call** A call is an unevaluated function, together with arguments that are
(Rmk:   .Call() is unrelated, calls C function)

### create a call
-   See:  R-lang 6.5, call, sys.call v match.call

```{r}
#| label: intro_call
#| collapse: true
#| include: true
f  <- function(x) {
    x^2}
cl  <- call("f", 3)
# display f as unevaluated f(3)
cl

##  Test for call.
    is.call(f)
    is.call("f")
    is.call(cl)

##  To evaluate a call.
    eval(cl)
```

Like symbol, expression, call is typeof 'language'.
```
three kinds of language objects that are available for modification, calls,
expressions, and functions
r-lang 6.1
```
is.call() is T only for calls. See: "in try... 4010_match_call_examples.Rmd"
***

**Calling environment of a function** To run, a function must be called.
Calling environment refers to environment of the calling function. Also called
parent environment. Not to be confused with a function environment. See example
??  The `calling function` is function actually making the call.
f = function()g()  # f is calling function

**Currying** Takes a function, partially evaluates, and returns as new
function. Example: f(x,y,z) evaluated at z=a, returns g(x,y) = f(x,y,a)

**context** internal, stack of C structs, track execution (see R Internals 1.4)
Allows flow control \| error reporting (traceback) \| sys.\* to work. (except
sys.status)

Closures create context.  internals do not. primitives only in special
situations. (sys.frame, sys.call count closures from either end of context
stack)  TODO  - do not understand.

Contexts are Not counted, not reported, not on stack, and coder has no
access to these functions.  REF:  R Internals 1.4

**byte code** "Readable" concise instructions; not machine code; no user
access; use JIT compiler or interpeter

**Deparse** See **parse**.

**defuse**
Synonym for capture unevaluated  code, stop immediate evaluation, 

**Evaluation or execution environment** In R, a function runs in an environment
specific to that function. Also referred to as frame or context. This frame
holds evaluation environment. The frame ends when the function completes.

**Evaluation**  parser, evaluator SEE R-lang definitions 2.1.3 
```
When a user types a command at the prompt (or when an expression is read from a
file) the first thing that happens to it is that the command is transformed by
the parser into an internal representation. The evaluator executes parsed R
expressions and returns the value of the expression. All expressions have a
value. This is the core of the language. 
```
 https://cran.r-project.org/doc/manuals/r-release/R-lang.html#Evaluation-of-expressions

**Expression** 


[R language definition](https://cran.r-project.org/doc/manuals/R-lang.html#Evaluation)
From r-lang 2.1.4 

|    In R one can have objects of type "expression". An expression contains one or
|    more statements. A statement is a syntactically correct collection of tokens.
|    Expression objects are special language objects which contain **parsed but
|    unevaluated R statements.** The main difference is that an expression object can
|    contain several such expressions. Another more subtle difference is that
|    objects of type "expression" are only evaluated when explicitly passed to eval,
|    whereas other language objects may get evaluated in some unexpected cases. 

(emphasis added)






Interactively, a single, valid R statement that returns an value is  called an expression. 


An expression also a formal language construction with list structure.  The function expression() takes an R
object and returns expression.  Note:  a `statement` is code that may do things
(side effects) but does not return anything.
Hadley defines expression as an "object that stores quoted code without evaluating it." (tidyr cheat sheet)
SEE evaluation.

from **Mailund** (metaprogramming, Chapter 3)
"Every statement you have in your programs is also an expression that
evaluates to some value (which, of course, might be NULL). This
includes control structures and function bodies. You can consider
everything an expression; it’s just that some expressions involve
evaluating several contained expressions for their side effects before
returning the result of the last expression they evaluate. From a
metaprogramming perspective, though, you are most interested in
expressions you can get **your hands on and examine, modify, or evaluate
within a program.**"
Examples:
```{r}
# expression examples:
rlang::is_expression(quote(x)) #T
rlang::is_expression(quote(1)) #T
rlang::is_expression(quote(x <- 3 + y))   #T
rlang::is_expression(quote(if (x  > z) print("yes")))   #T

# body of function
rlang::is_expression(body(f = function() x^y))   # T

# manipulate expression:
e= quote(x + y + z)  # x + y + z
length(e)   # 3

e[[3]]  <- quote(z + 3)
e # x + y + (z + 3)
```

**Expression v Language** R expressions based on list and can be broken down
further. Often these are language pieces. Lanugage use pairlists.

**First Class** - A function can also be used as an argument to another
function. Example: lapply(list(), mean)

**Frame vs Environment** Frame refers to the calling stack of functions.
Environment, in R, is property of function, where it looks to find non-local
variables.

**Function, properties** formals(f) arguments in function defintion body(f)
code environment(f) finds values of non-formal (non-local) variables where the
function was created. **Higher Order Function** Function that takes another
function as an argument and ...

**immutable**

**Interactive vs. Non-Interactive** R, or S, originally designed to be
interactive, ie command and response at console. .R, .Rmd, Rscript, R CMD BATCH
(TODO: some error conditions do not work in BATCH ??)

**Lambda Calculus** Instead of naming function (f(x,y) = x\^2 + y\^2) create
abstraction. (x,y) --\> x\^2 + y\^2. Or instead of g(x) = x + 2; write
lambdax.x+2. Easy to chain

**Lexical Scope** How R function finds *unbound* variables: in environment
where function was created. **Dynamic Scope** Method to find variables in Call
Stack at runtime. R uses Lexical Scope, however the R Language allows coder to
select environment to evaluate variables. (REF: June Choe Slack/Nov 3 2021)

Scheme added (?) Portion of code in which binding applies to a variable??

In R, an "evaluator" find any "unbound symbols" (in an expression) by using
variable bindings in effect when created.

**match** - match.arg - match.call - match.fun

**namespace:**
REF: https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Namespaces
Namespaces are *environments* associated with packages ( + base pkg,
special) A package pkg defines two environments namespace:pkg and
package:pkg: it is package:pkg that can be attached and form part of
the search path.

- Tieryn(2003) http://homepage.divms.uiowa.edu/~luke/R/namespaces/morenames.pdf

examples:   SEE 9009_

Treat code as data:   ability to manipulate code before evaluated.
**NSE, Non-Standard Evaluation**
- https://edwinth.github.io/blog/nse/
- https://thomasadventure.blog/posts/understanding-nse-part1/  $ (uses NSE), [[ (does not)

**Standard evaluation**
In se expressions are evaluated immediately, ie the code and all variables are
found  the value is inserted.   (SEE Brodie, rev() example)

**operator** (non-R) An operate takes a function f and returns new function g.
Example: $f'(x) = g(x)$

**package:**

**Pairlist**

**Parent Frame of function** If function g() is called inside body of function
f, the g has the parent frame (aka calling environment) that is execution
environment of f. DRAW Diagram

**Parse** 
Convert a string (character vector) into an R Expression (ie code), which is
NOT a string. Motivation is to setup R object for manipulation *before*
evaluation. Parse(\*.R) removes comments. Note:  after parsing, the result is
NOT character(1), a string.

**Deparse** converts an R Expression to a string (character vector) .
```{r}
x="a + b"
parse(text=x)   # expression(a+b)

# but, does not evaluate, b/c it quotes immediately
lobstr::ast(parse(text=x))

# 
lobstr::ast(parse(text=!!x))
?ast
```

Parse & Deparse are NOT? opposites. See Murdoch

(latex) parse: string ==`>` R expression (error if invalid) deparse: R
expression ==`>` string (actually: structure(expression(), scrfile)

**options** Temporary vs global vs local. Read R manual.(TODO)

\subsection{Primitive vs Internal function}

-   `if`, `+`, sin, sqrt

-   C functions

-   SEE ADV-R Chapter 6, code: 059 (myoldcode)

-   SEE https://nsaunders.wordpress.com/2018/06/22/idle-thoughts-lead-to-r-internals-how-to-count-function-arguments/

-   SEE R Internals/Ch 2

-   Do not understand at deeper level

```{r }
#| label: primitive 
#| include: true
#| eval: false

#   TODO
#   R complains about putting function in data.frame

### check several functions
y  <- list(sin, "sin", c, switch, typeof, sqrt, `if`, `+`)

quote(sin)
quote("sin")
quote(c)
quote(sqrt)
quote(`if`)
quote(`+`)
deparse(y)
data.frame(object = y,
           typeof = sapply(y, typeof),
           is.primitive = sapply(y, is.primitive),
           is.function = sapply(y, is.function))
```

**R** R has two parents: S, based on C, Fortran for statistics. R also has
functional component, based on Scheme.

```         
It is possible to abuse R, using it more like S code. (?)

**Reification** Abstract idea to treat all code as "data", including functions, structures, etc. This means all such objects can be modified by code. C has. (TODO)


**  Referencial Transparency

A function f is \textbf{referencial  transparent} IF replacing x (an expression) with its value
returns same.

```{r}
f = function(x) x
x = 6
identical(f(x), f(6))
```

However, not all R functions have this property.
```{r}
x=6
identical(quote(x), quote(6))               ##  F
```

**Referencial Semantics** Changes to values are done in memory. There is no
copy.   (Example:  why important.   Also other properties of functions, inverse, etc)

**Search List**
Heirarchy of packages:  First is globalenv, followed by packages in reverse order.
Loading a package not necessary attach.
library() will load and attach.

**side effect**
A function may access global and formal variables read-only.  Only local variables may be modified.
-   a popup? console output? no changes to files, no graphs

**srcref**
Is an attribute of all functions.  The body() contains code only.   The srcref
contains original code, plus comments and formatting.


**Substitution** When used in function with formal variable, substitute stops
evaluation, captures the user's code and returns a call (ie unevaluated )

|   substitute returns the parse tree for the (unevaluated) expression expr, substituting any variables bound in env.

**syntax** How code looks, is { in right place, a grammar.

**Syntax Sugar** Syntax to make easier for human to express or write code
efficiently.


**semantics** What does the code DO?

**String** String ("5+5") is NOT call. No such thing as evaluating a string.
See 0210\_ You can PARSE a string and then manipulate it. Simpler to eval a
quote(5+5) to return the sum.

**String Interpolation**

Method to substitute the value of expr into a string. Can think of it as `template` with holes.
SEE: https://www.r-bloggers.com/2018/03/math-notation-for-r-plot-titles-expression-and-bquote/

bquote examples  SEE 410
```{r}
x = 5 
bquote(x == .(x))
```

### Symbol

[3.1.2 Symbol lookup](https://cran.r-project.org/doc/manuals/r-release/R-lang.html#Symbol-lookup) 
| In this small example y is a symbol and its value is 4. A symbol is an R object too, 

Q:  This is true, mathematically:    a*(b+c) = a*b + a*c.   In practice, I get
to choose to evaluate (insert values) with the LHS  or the RHS, expecting the
exact same result had I done the other.  Relationship to Symbol in
Metaprogramming?

**symbol** - human readale, points to area in memory, immutable, not a
string, not a value, not set of instructions.  In LISP (and R?) you
EVALUATE symbols to get a value.

stored in a lookup table?   Two symbols can be compared, if equal then same memory.
(is symbol evulated ??)
SEE: https://stackoverflow.com/questions/8846628/what-exactly-is-a-symbol-in-lisp-scheme

```{r}
y = 4
y
is.symbol(y)
is.name(y)
is.object(y)

# but
y = as.symbol(y)
is.symbol(y)
y
```

See **R Lang Ref: 2.1.3.1**   Symbol (aka name), usually name of R object.  Use
`as.name() to coerce to symbol or quote() or atoms of parse()

```
In order to manipulate symbols we need a new element in our language: the
ability to quote a data object. Suppose we want to construct the list (a
b). We can’t accomplish this with (list a b), because this expression
constructs a list of the values of a and b rather than the symbols
themselves. This issue is well known in the context of natural languages,
where words and sentences may be regarded either as semantic entities or as
character strings (syntactic entities). The common practice in natural
languages is to use quotation marks to indicate that a word or a sentence
is to be treated literally as a string of characters. For instance, the
first letter of “John” is clearly “J.” If we tell somebody “say your name
aloud,” we expect to hear that person’s name. However, if we tell somebody
“say ‘your name’ aloud,” we expect to hear the words “your name.” Note that
we are forced to nest quotation marks to describe what somebody else might
say. We can follow this same practice to identify lists and symbols that
are to be treated as data objects rather than as expressions to be
evaluated. However, our format for quoting differs from that of natural
languages in that we place a quotation mark (traditionally, the single
quote symbol ’) only at the beginning of the object to be quoted. We can
get away with this in Scheme syntax because we rely on blanks and
parentheses to delimit objects. Thus, the meaning of the single quote
character is to quote the next object. Now we can distinguish between
symbols and their values:

```
https://stackoverflow.com/questions/8846628/what-exactly-is-a-symbol-in-lisp-scheme
##  Tidy Evaluation
-   pronouns, to distinguish between objects in environment ls() .env$cyl and
  not associated with the df and data columns in df .data$cyl (df)

**Variable** Three kinds:\
\* formals,x:    f = function(x= ... )\  formalArgs()
\* local,a:       f = function() {a =10}\
\* free, unbound, global, z:    f = function() (print(z))

------------------------------------------------------------------------

**function**

```{r function}
f  <- function(x=NULL) {
    x^2
}

formals(f)      ## pairlist
body(f)         ## language, $\code{call}$
environment(f)  ## environment

args(f)         ## closure
```

```{r parse}
## returns expression
parse(text= '2^2')

## fails, does not know a is.
# parse(text= '2a')
```
**call**
```{r call}
f  <- function(x=NULL) {
}

cl
cl  <- call("f", list(x=2))
is.function(cl)
is.call(cl)


##  Args must be evaluated, even if f is unevaluted 
    x  <- 2
    call("f", list(x))
    #call("f", list(x=a))   # throws error
```

```{r sub}
res  <- substitute(x+a) 
res
is.call(res)
```
:::

##  Questions
```{r}
#   Explain how Base R finds column name
library(dplyr)
data(starwars)
col = "hair_color"
sum(is.na(starwars[, eval(col) ]) )
sum(is.na(starwars[, col ]) )
```

## {{< include _meta_questions.qmd >}}

####    K-nearest neighbors, K is given

$\forall x \in X$ , which could be any dimension , is already assigned to a region.
For a new point, examine its K nearest neighbors who decide by majority vote which region $x$ belongs to.
SEE:  wine example
SEE:  Gaglow book.

####    Bias-Var Tradeoff.
With non-zero `noise`, of variance $\sigma^{2}$  the best approximate to $f(x)$ will always have non-zero error:
Isn't there a relation betwee E, VAR?    like x and p ?

$$
Error = E(f_hat) + Var(f_hat) + \sigma^{2}
$$


SEE Berkeley Crash Course; Matloff

### 2023-05-16,  Why Rlang?  to june
I'm in rlang book club, not up-to-date, and debating WHY? work through rlang::
I think more logical to approach rlang as follows:

(1)learn *some* lisp (scheme), then (2) learn base R (as language,  to manipulate), and only
(3) then work through rlang:: *code* as an EXAMPLE of magic one can do with lanuage.

If you have time and willing,  feel free to answer to the entire group, if you wish.
Or, you are  too busy, don't worry about reply.   I think others have similar questions.

Here are few points that might clarify where I am:

-   R about 4 years, including tidyverse 
-   struggle with rlang:: not because ideas are especially difficult but
  becuase I find package to be verbose, with imprecise definitions and built
  upon a structure of many other packages.  And I do not have all the ideas
  nailed down.
-   the ideas, once I draw picture or think a bit, seem very logical, useful and *cool*  (or do I fool myself?)
-   So not why focus on ideas first (ie scheme or equivlent),  then see how R implements, and then build something new.
-   Me:   minimal C;  minimal Lisp.
-   But baffled why so much time being  spent on *.data[[]]*, pronouns, new notation.   What is wrong with just bquote?   And if bquote doesn't cut it in certain instances show why *.data[[]]*
code improves upon bquote.
-   I've also tried to write a glossary + code examples for each metaprogramming idea in base R (but only got more confused)
    

## section{R}

	

###		R, DEFINTIONS, TERSE EXAMPLES
			See ~/code/try_things_here/BASE/

####    R, Definitions
-   **object**  Most computer languages do NOT allow direct access to
    memory.  In R, various data structures (called `Objects` provide
    access.  Use symbols or variables to access the the `Objects`.
    Unique to R(?), symbols are also objects and can be manipulated
    (example?).

-   **intrepreted vs compiler code**   The former is source code that
    is executed line-by-line.   The later is machine code.   Between
    the two, is wide spectrum

-   **struct** (C, non-R)  a collection that can hold multiple types, eg `db
    record`.

```
    struct record
    {
        char name[32];
        int age;
        float debt;
    }
#   To use:
    struct record X    # X is variable, struct is keyword, `record` is struct
```

-   **monad** - As goal, seek functions with (1) no side effects (2) can
    be composed.  Function factories can be useful, esp where variables can be
    'stored' in environment.   SEE BRUNO video.

}


### Shiny and DT
- embed html, see !so 69471577

```
## Bugzilla < https://bugs.r-project.org/ >
-	Besides R bugs good place to see intersection of documentation, R and bugs.

-	<https://vroom.r-lib.org> package uses new internal data structure *ALTREP* <https://www.r-project.org/dsc/2017/slides/dsc2017.pdf>

	 	
***

::: {.callout-note}
All R, math, statistics  notes here. 
:::

[call](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/call.html)
[expression](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/expression.html)
[language](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/is.language.html)

[mode]](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/mode.html)
[typeof](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/typeof.html)
[vector](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/vector.html)
[substitute](https://stat.ethz.ch/R-manual/R-devel/RHOME/library/base/html/substitute.html)


## {{< include _future_work.qmd >}}
## Environemnts, Namespacds
-   conflicted package.

#{{< include _references.qmd >}}
```

### parquet, database (r4ds Chapter 22)
- parquet file is now popular, esp large datasets (csv too slow)
- Arrow package set of tools; to convert csv to parquet; to translate queries from dplyr and run them againt parquet

### Following `References` was removed and now added back (11/2024)...

### Metaprogramming, NSE  

-   Hadley, Advanced R, version 1 (Expressions)
-   Quoting/Eval:  Lionel: https://rpubs.com/lionel-/programming-draft  
  -   https://rpubs.com/lionel-/tidyeval-introduction
  -   https://rpubs.com/lionel-/tidyeval-dplyr-recipes
  -   {{}} * https://www.tidyverse.org/blog/2019/06/rlang-0-4-0/
  -   https://rpubs.com/lionel-/superstache
    Brodie Gaslam
    -   https://www.brodieg.com/2020/05/05/on-nse/


### Articles

-   Quoting/Eval:  Lionel: https://rpubs.com/lionel-/programming-draft  
  -   https://rpubs.com/lionel-/tidyeval-introduction
  -   https://rpubs.com/lionel-/tidyeval-dplyr-recipes
  -   {{}} * https://www.tidyverse.org/blog/2019/06/rlang-0-4-0/
  -   https://rpubs.com/lionel-/superstache
    Brodie Gaslam
    -   https://www.brodieg.com/2020/05/05/on-nse/
-   https://www.rostrum.blog/2023/03/03/getparsedata/ (parse, tokens,  more advanced)
-   https://renkun.me/2020/11/08/using-parse-data-to-analyze-r-code/ (parse(), XPATH, rlanguage server)

-   function masking/pkgs: https://www.r-bloggers.com/2013/09/control-the-function-scope-by-the-r-package-namescope/ (using namespace to control scop)
-   {}} - https://www.r-bloggers.com/2019/06/curly-curly-the-successor-of-bang-bang-2/
-   env stack - https://www.r-bloggers.com/2014/12/tips-on-non-standard-evaluation-in-r/
-   quoting, dplyr - https://www.r-bloggers.com/2019/07/bang-bang-how-to-program-with-dplyr/
-   2012 namespace pkg, by Hadley, et al : https://cran.r-project.org/web/packages/namespace/index.html

-   **Examples**
  - http://zevross.com/blog/2018/09/11/writing-efficient-and-streamlined-r-code-with-help-from-the-new-rlang-package/ (mostly ggplot2)
  - Murdoch,  R Journal vol 2/2 2010
  - statisticsglob.com (several parse examples)
  - <https://statisticsglobe.com/parse-deparse-expression-r-function>
  - <advanced-r-solutions.rbind.io/expressions.html>
  - Tierney, codeTools ?

### Manuals:
  - R-exts:package-ns: https://cran.r-project.org/doc/manuals/R-exts.html#Package-namespaces
  - R-ints 
        -   1.2 https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Environments-and-variable-lookup
        -   1.4 C structs, Contexts  (https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Contexts)
        -   1.5 When is argument evaluated?
    R-Lang <https://cran.r-project.org/doc/manuals/R-lang.html>   
        -   2.1.3 Language Objects (calls, expressions, names)
        -   3   Evaluation
        -   6 Compute on Language: https://cran.r-project.org/doc/manuals/r-release/R-lang.html#Computing-on-the-language
  - ns-load: https://stat.ethz.ch/R-manual/R-devel/library/base/html/ns-load.html
  - getFromNamespace: https://stat.ethz.ch/R-manual/R-devel/library/utils/html/getFromNamespace.html

-   **stackoverflow**

  - https://stackoverflow.com/questions/46834655/whats-the-difference-between-substitute-and-quote-in-r
  - https://stackoverflow.com/questions/14988722/in-r-what-does-loaded-via-a-namespace-and-not-attached-mean
  - {{}}https://stackoverflow.com/questions/62791997/what-is-the-embracing-operator
-   
-   **Posit**
  - ns, but not in package: https://community.rstudio.com/t/is-it-dangerous-to-create-a-namespace-for-functions-in-a-script-without-a-package/91141

### Packages using metaprogramming; environments
    -   wrapr https://winvector.github.io/wrapr/index.html useful?
    -   lintr  (parses)
    -   rlangserver
    -   envnames:: code for working with env, older https://github.com/mastropi/envnames
    -   

https://statisticsglobe.com/parse-deparse-expression-r-function
### LISP & R

Holiday Reading !??

Many years ago, one of my freshman college roommates walked in the door speaking high praises for LISP.  
For some of us, it takes a longer to catch on.  Over the weekend, I read through the
"EVAL" chapter (Chapter 3) of Common LISP ( https://www.cs.cmu.edu/~dst/LispBook/)
(Tourteszky, Introduction to Common LISP - 1990).  

"So that's what R is trying to do!"  

Seems that LISP is cleaner way to introduce the
many list-like structures of R and how they built, passed, evaluated
or otherwise manipulated.

Then I read a chapter of this book and it too greatly helped with R.   More light bulbs went on.

Metaprogramming in R
(https://www.amazon.com/exec/obidos/ASIN/1484228804/acmorg-20) by
Thomas Mailund (also:


More from Thomas Mailund:
https://mailund.github.io/r-programmer-blog/2018/09/20/scoping-rules-and-nse/)

