
---
title: Template for .Rmd
output: 
  pdf_document:
    latex_engine: xelatex
    toc:  TRUE
    toc_depth:  1
fontsize: 12pt
geometry: margin=0.5in,top=0.25in
#  md_document:
#  html_document:
#    toc: true
#  	toc_float: true
#    css: styles.css
---

---
/home/jim/.config/nvim/templates/skeleton.Rmd
othercomments
---

<!--  commments -->

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  comment="      ##",  error=TRUE, collapse=TRUE)
```

```{r library, include=FALSE		}
library(jimTools)
library(here)
```


```{r render, eval=FALSE	}
here()
file <- "005_rmd_examples.Rmd"
file  <- basename(file)
dir=""

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```








list?

- one 
- two
- three

***

list?
* one
* two
* three
*

*** 

list?
* one 
*
* two
*
* three
*

***
list?
-	one 
-	two 
-	three

***
list?
	-	one
	- two
	- three
	

***

>	is this block?
***

	
` code block ` 
*** 

### Verbatim quote

`this is a quote, but does not appear so`

`"this is also a quote and appears so."`


This is regular text.

>		But this should be an indented block.  And this also should be part of the
>		indent.   Let us add one more sentence to see if three or more sentenaces
>		are also in the block.    All have '>' in first column.
>
>
>

```{r knit_exit()} knitr::knit_exit() ```
